Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-07 longSC.tex
EKRT

\subsection{Higher Order Harmonic Correlations}
The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical model calculations. 
The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}. 
While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$, only two calculations with the parameters which describe the lower order harmonic correlations better are compared to the higher order harmonic correlations. The other calculations show a quite clear deviation from the data. 
As it is seen in Fig.~1 from Ref.~\cite{Niemi:2015qia} that the temperature at the minimum of $\eta/s$ for "param1" (at $T$ = 150~MeV) is smaller than the other parameters used. The model calculations with the parameters whose temperature at the minimum of $\eta/s$ is larger than "param1" can be ruled out.
As shown in Fig.~\ref{fig:Figure_5}, the correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are well described. The model calculations give better description than the correlations between $v_4$ and $v_2$. 
In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the data significantly like the correlation between $v_3$ and $v_2$.

>>>>

\subsection{Higher Order Harmonic Correlations}
\label{sec:theory_highorder}
The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical model calculations. 
The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}. 
While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations better are compared to the results of higher order harmonic correlations. The other calculations show a quite clear deviation from the data. 
As it is seen in Fig.~1 from Ref.~\cite{Niemi:2015qia} that the temperature at the minimum of $\eta/s$ for "\textit{param1}" (at $T$ = 150~MeV) is smaller than the other parameters used. The model calculations with the parameters whose temperature at the minimum of $\eta/s$ is larger than "param1" can be ruled out.
As shown in Fig.~\ref{fig:Figure_5}, the correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are well described by those two model parameters within the errors.  The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the data significantly like the correlation between $v_3$ and $v_2$.

%\begin{figure*}[!]
%            \begin{center}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT.eps}}
%                \end{center}
%        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
%        \label{fig:Figure_5_0}
%\end{figure*}
